Exploring Design Space for Differentially Private Bayesian Inference

### 2019-01-05 ICML2019/main.tex
update accuracy

\subsection{Accuracy Comparison between $\hexpmech$, $\lapmech$ and $\ilapmech$}
For comparison with Laplace mechanism, we developed the Table \ref{tab_acc_theo}.
\begin{table*}[t]
\scriptsize
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 c & 0 
 & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
    \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
 & $1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
 \hline
 $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
 & 0.19673467014 & 0.11932560927 & 0.07237464051 \\
 \hline
 $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & 0.31606027941 & 0.11627207896 & 0.04277410743 \\
 \hline
 $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & $\frac{1}{\nomalizer{\dataobs}}$
 & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
 \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$
 & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$\\
 \hline
\end{tabular}
\caption{Accuracy Comparison in Theoretical}
\label{tab_acc_theo}
\end{table*}

In the case when $\alpha = \beta$, there are always 2 symmetric beta distributions with the same distance from the true posterior, then we have accuracy table as:
\begin{table*}[t]
\scriptsize
\centering
\begin{tabular}{ |c|c|c|c| } 
\hline
 c & 0 
 & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
  & $1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$  \\
 \hline
 $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
 & 0.19673467014 & 0.31606027941 & 0.19170024978 \\
 \hline
 $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & 0.31606027941 & 0.43233235838 & 0.1590461864 \\
 \hline
 $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
 & $\frac{1}{\nomalizer{\dataobs}}$ 
 & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} 
 \cdot
 \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ 
 & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$\\
 \hline
\end{tabular}
\caption{Accuracy Comparison in Theoretical}
\label{tab_acc_theo}
\end{table*}

@@

By solving following equations:
  \[
  \frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
  \]
  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer. 
  \[
  \frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
   = 0.119325609\ or\ 0.116272079
  \]
  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
  \[
\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
     = 0.072374641\ or\ 0.042774107
\]
we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one... etc.

>>>>

\subsection{Accuracy Comparison between $\hexpmech$, $\lapmech$ and $\ilapmech$}
For comparison with Laplace mechanism, we developed the Table \ref{tab_acc_theo}. In this table, the first column is the value of distance $c$ from the correct posterior distribution. The first row is three mechanisms: $\lapmech$, $\ilapmech$ and $\hexpmech$. For each mechanism, we calculate the probability of outputting corresponding candidates which is at distance $c$ from the correct posterior distribution and put into the table. We calculate the first three nearest candidates and the others trival.
\begin{table*}[t]
\scriptsize
\centering
\caption{Accuracy Comparison in Theoretical}
\label{tab_acc_theo}
\begin{tabular}{ |c|c|c|c|c| } 
\hline
 c & 0 
 & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
    \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
 & $1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$ & \dots  \\
 \hline
 $\lapmech $
 & 0.19673467014 & 0.11932560927 & 0.07237464051 & \dots \\
 \hline
 $\ilapmech $
 & 0.31606027941 & 0.11627207896 & 0.04277410743 & \dots \\
 \hline
 $\hexpmech $
 & $\frac{1}{\nomalizer{\dataobs}}$
 & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
 \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$
 & $\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ & \dots\\
 \hline
\end{tabular}
\end{table*}

% In the case when $\alpha = \beta$, there are always 2 symmetric beta distributions with the same distance from the true posterior, then we have accuracy table as:
% \begin{table*}[t]
% \scriptsize
% \centering
% \begin{tabular}{ |c|c|c|c|c| } 
% \hline
%  c & 0 
%  & $1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
%   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}$
%   & $1 - 
%     \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%     \cdot
%     \sqrt{1 - \frac{\frac{t}{2}}{\beta}}$ & \dots  \\
%  \hline
%  $\lapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z ) = c} $
%  & 0.19673467014 & 0.31606027941 & 0.19170024978 & \dots \\
%  \hline
%  $\ilapmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
%  & 0.31606027941 & 0.43233235838 & 0.1590461864 & \dots \\
%  \hline
%  $\hexpmechPr{\dataobs}{\hellinger(\bysinfer(\dataobs), z) = c}$
%  & $\frac{1}{\nomalizer{\dataobs}}$ 
%  & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} 
%  \cdot
%  \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ 
%  & $\frac{2 \exp{(\frac{- \epsilon \sqrt{1 - 
%     \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
%     \cdot
%     \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
%     {4 S(\dataobs)})}}{\nomalizer{\dataobs}}$ & \dots \\
%  \hline
% \end{tabular}
% \caption{Accuracy Comparison in Theoretical}
% \label{tab_acc_theo}
% \end{table*}

@@

By solving following equations:
  \[
  \frac{1}{\nomalizer{\dataobs}} = 0.19673467\ or\ 0.316060279
  \]
  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the correct answer. 
  \[
  \frac{\exp{(\frac{- \epsilon \sqrt{1 - \frac{\Gamma(\alpha+\frac{1}{2})}{\Gamma(\alpha)} \cdot
   \frac{\Gamma(\beta - \frac{1}{2})}{\Gamma(\beta)}}}{4 S(\dataobs)})}}{\nomalizer{\dataobs}}
   = 0.119325609\ or\ 0.116272079
  \]
  we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with one step from correct one.
  \[
\frac{\exp{(\frac{- \epsilon \sqrt{1 - 
    \sqrt{1 - \frac{\frac{t}{2}}{a + \frac{t}{2}}}
    \cdot
    \sqrt{1 - \frac{\frac{t}{2}}{\beta}}}}
    {4 S(\dataobs)})}}{\nomalizer{\dataobs}}
     = 0.072374641\ or\ 0.042774107
\]
we can get the range where we can do better than $\lapmech$ or $\ilapmech$ on outputting the answer with two steps from the correct one... etc.
